The Post-2007 Declining U.S. Birth Rates imply Significant Societal Shifts in the U.S.

### 2023-02-22 outputs/paper/paper.qmd
Add files via upload

```{r setup, include = FALSE}
#Load libraries
library(gridExtra)
library(cdlTools)
library(RGraphics)
library(tidyverse)
library(palmerpenguins)
library(knitr)
library(ggplot2)
library(haven)
library(dplyr)
options(dplyr.summarise.inform = FALSE)
```

@@

# Discussion

>>>>

```{r setup, include = FALSE}
#Load libraries
library(gridExtra)
library(cdlTools)
library(RGraphics)
library(tidyverse)
library(palmerpenguins)
library(knitr)
library(ggplot2)
library(haven)
library(dplyr)
library(expss)
options(dplyr.summarise.inform = FALSE)
```

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: tbl-1
#| tbl-cap: change in birth rate by age group

numbirth_2044 <- read.csv(here::here("inputs/data/educ/numbirths_educ_2044.csv"))
numbirth_2044 %>% 
  kable(col.name=c("Age Group","Birth Rate Chage"),booktabs = TRUE,show_col_types=FALSE,linesep="")
```

\newpage
# Discussion
